---
title: "Compile Hadley’s Advanced R to a PDF"
author: "Mo ruizhe"
date: "2020/3/21"
output:
  pdf_document: default
  html_document: default
---
### Download the Source: 
https://github.com/hadley/adv-r.git
### Install R Package dependencies
```{r eval=FALSE}
devtools::install_github("hadley/sloop")
devtools::install_github("hadley/emo")
```
# failed to install "emo"packages
solutions:
```{r eval=FALSE}
$ git config --global http.sslBackend"openssl"
$ git config --global http.sslCAInfo [path to .pem file]
```
# lack some packages
solutions:
installed the following packages,named DBI,RSQLite,dplyr,ethuis,profvis,bench.
# Quitting from lines 223-235 (Introduciton.Rmd)
solutions:
Adding encoding = "UTF-8" in line 224 can fix it.
```{r eval=FALSE}
contributors <- read.csv("contributors.csv", stringsAsFactors = FALSE, encoding = "UTF-8")
```
# latex fail to compile...
solutions:
```{r eval=FALSE}
update.packages(ask=FALSE,checkBuilt=TRUE)
tinytex::tlmgr update()
```
# Fonts cannot be found
solutions:
download "Inconsolate"和 "Andale Mono"